---
title: "R for Data Science (Hadley Wickham) - Chapter 17 Exercises"
output: html_document
---

## 17 Intro Exercises
### Write For Loops to 
####a Compute the mean of every column in mtcars
```{r 171a, include=TRUE}
means <- vector("double", length(mtcars))
for (i in seq_along(mtcars)){
  means[[i]] <- mean(mtcars[[i]])
}
means
```

####b Determine the type of each column in nycfilghts13::flights
```{r 171b, include=TRUE}
types <- vector("character", length(nycflights13::flights))
for (i in seq_along(nycflights13::flights)){
  types[[i]] <- typeof(nycflights13::flights[[i]])
}
types
```

####c Compute the number of unique values in each column of iris.
```{r 171c, include=TRUE}
vals <- vector("integer", length(iris))
for (i in seq_along(iris)){
  vals[[i]] <- dplyr::n_distinct(iris[[i]])
}
vals
```

####d Generate 10 random normals for each of Mu = -10, 0, 10, and 100. Think about the output, sequence, and body before you start writing the loop.
```{r 171d, include=TRUE}
# Output will be vector of 4 lists of 10 doubles
# Sequence is along a manually inputted list of Mus
# Body just generates a list of 10 randoms
mus <- c(-10, 0, 10, 100)
output <- vector("list", length(mus))
for (i in seq_along(mus)){
  output[[i]] <- rnorm(10,mus[[i]])
}
output
```

####2 Do the previous 4 for loops with purrr::map_* instead
```{r 172, include=TRUE}
library(tidyverse)
means <- mtcars %>%
  map_dbl(mean)
means

types <- nycflights13::flights %>%
  map_chr(typeof)
types

vals <- iris %>%
  map_int(n_distinct)
vals

output <- c(-10, 0, 10, 100) %>%
  map(rnorm,n=10)
output
```